A Global Picture of Food Insecurity and Hunger

### 2020-09-11 docs/modeling_fies.tex
Account for Covid

\subsection{Disaggregation}
Assumptions

@@

\subsection{Component Questions of the FIES}
\begin{enumerate}
	\item During the last 12 MONTHS, was there a time when you were worried you would not have enough food to eat because of a lack of money or other resources?
	\item Still thinking about the last 12 MONTHS, was there a time when you were unable to eat healthy and nutritious food because of a lack of money or other resources?
	\item Was there a time when you ate only a few kinds of foods because of a lack of money or other resources?
	\item Was there a time when you had to skip a meal because there was not enough money or other resources to get food?
	\item Still thinking about the last 12 MONTHS, was there a time when you ate less than you thought you should because of a lack of money or other resources?
	\item Was there a time when your household ran out of food because of a lack of money or other resources?
	\item Was there a time when you were hungry but did not eat because there was not enough money or other resources for food?
	\item During the last 12 MONTHS, was there a time when you went without eating for a whole day because of a lack of money or other resources?
\end{enumerate}

\end{document}

>>>>

\subsection{Disaggregation}
The data on the FIES collected by Gallup

Assumptions

@@

\subsection{Component Questions of the FIES}
\begin{enumerate}
	\item During the last 12 MONTHS, was there a time when you were worried you would not have enough food to eat because of a lack of money or other resources?
	\item Still thinking about the last 12 MONTHS, was there a time when you were unable to eat healthy and nutritious food because of a lack of money or other resources?
	\item Was there a time when you ate only a few kinds of foods because of a lack of money or other resources?
- out-of-sample fit also very good, r2 around 0.99

- variable importance and coefficient table?

\section*{Supplemental Info}
